---
title: "CAPM_example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We first scrape some daily stock trading data from yahoo. Here “^GSPC” is SP500, “BAC” is
Bank of America, “VFINX” is a mutual fund that is aimed to track the SP500 index. “VBIND”
and “FDAFX” are two other mutual funds that we will talk about in details later. We start from
2004 because FDAFX went on market in the mid of 2003.
We also get the 3-month interest rate from FRED. Different from our last R example file where
we downloaded monthly interest rate data, this time we need daily data (of the annual yield of 3-
month T-bills) so that stock data and bond data are of the same frequency.


```{r , echo= FALSE}
rm(list=ls())
library("quantmod") 
getSymbols(c( "^GSPC","BAC", 'VFINX',"VBINX","FDAFX"),src="yahoo", from = '2004-01-
01', to = '2019-04-30')
getSymbols("DGS3MO", src = "FRED")
```

Next, we combine data from the two sources into one new data frame called “data”. We also
rename each variable in it (with a simpler variable name).

```{r , echo= FALSE}
data <-
merge(GSPC$GSPC.Close,BAC$BAC.Close,VFINX$VFINX.Close,VBINX$VBINX.Close,FDAFX$FDAFX.Cl
ose,DGS3MO['2004::2019-04'])
names(data) <- c("SP500","BAC","VFINX", "VBINX","FDAFX","DGS3MO")
````
The merged data frame shows some missing values from days of market closure. (Note the stock
market and the bond market also have a slightly different set of closure dates.) In this example
we decide to get rid of all days that at least one market is closed.

```{r , echo = FALSE}
colSums(is.na(data))
data<-na.omit(data)
colSums(is.na(data))
```

